%*******************************************************
% Acknowledgements
%*******************************************************
\pdfbookmark{Acknowledgements}{Acknowledgements}

\chapter*{Acknowledgements}
\label{chp:ack}

First and foremost, I thank Axel Borst for being an inspiration, a role model, and a guide throughout these formative years. He taught me a unique way of thinking about both neural circuits and science in general (as well as filter theory which I suspect precedes them all). Through his approach, Axel fosters an atmosphere of curiosity, creativity, and intellectual camaraderie that I can only hope to carry forward. Not a day goes by without considering myself lucky to be part of his team.

Many have accompanied me on this scientific journey. In no particular order, I thank
Armin Bahl for teaching me how to tackle a problem;
Hubert Eichner for spotting non-answers from a distance;
Georg Ammer for knowing everything I didn't;
Michael Drews for a demonstration of how to immerse yourself in science;
Florian Richter, Anna Schützenberger, and Sandra Fendl for spirited discussions and general loveliness;
Isabella Kauer for steering me back toward music;
Alexander Arenz for an unquenchable enthusiasm in all things science;
Alex Mauss for being on top of things;
Jürgen Haag for having been on top of things since before I was born;
Franz Weber for an introduction to theoretical patch clamp;
Stefan Prech for technical ideas and skill at turning them into useful tools;
Ruben Portugues and Stefan Glasauer for their advice as part of a belated thesis committee;
Romina Kutlesa and Christian Theile for their support with experiments;
everyone in our group for making it a little bubble of joy both scientific and not;
everyone at the Max-Planck-Institute for turning these grey walls into a place worth missing;
and most importantly Matthias Meier and Etienne Serbe for things too numerous to write down.

Alex, Alexander, and Matthias kindly read and greatly improved this thesis. I remain indebted to the administrative team of the Graduate School for Systemic Neurosciences.

For supporting me throughout these years, I am grateful to all friends not named so far and of course my family. Finally, I thank Emilia Geiger for everything; without her, these pages would be empty.