\chapter*{Contributions}

\begin{itemize}
    
    \item Maisak MS, Haag J, Ammer G, Serbe E, Meier M, \textbf{Leonhardt A}, Schilling T, Bahl A, Rubin GM, Nern A, Dickson BJ, Reiff DF, Hopp E, Borst A (2013). A directional tuning map of \textit{Drosophila} elementary motion detectors. \textit{Nature} 500(7461):212-6.
    
    \begin{itemize}
        \item
        % \paragraph{Contributions}
        M.S.M. and J.H.\ jointly performed and, together with A.Bo., evaluated all calcium imaging experiments. G.A., E.S.\, M.M.\ recorded from tangential cells. \textbf{A.L.}, T.S. and A.Ba.\ performed the behavioral experiments. G.R., B.D.\ and A.N.\ generated the driver lines and characterized their expression pattern. D.F.R.\ performed preliminary imaging experiments. E.H.\ helped with programming and developed the PMT shielding for the two-photon microscope. A.Bo.\ designed the study and wrote the manuscript with the help of all authors. M.S.M.\ and J.H.\ contributed equally to this article.
    \end{itemize}
    
    \item Ammer G, \textbf{Leonhardt A}, Bahl A, Dickson BJ, Borst A (2015). Functional Specialization of Neural Input Elements to the \textit{Drosophila} ON Motion Detector. \textit{Current Biology} 25(17):2247-53.
    
    \begin{itemize}
        \item
        % \paragraph{Contributions}
        G.A.\ and A.\ Borst designed the study. G.A.\ performed electrophysiological experiments and anatomical characterization of expression patterns, analyzed the data, and wrote the manuscript with the help of A.\ Borst, \textbf{A.L.}, and A.\ Bahl. \textbf{A.L.}\ and A.\ Bahl performed behavioral experiments and analyzed data. B.J.D.\ generated SplitGal4 fly lines and hosted G.A.\ for characterization of Gal4 lines. A.\ Borst performed computational modeling.
    \end{itemize}
    
    \item Serbe E, Meier M, \textbf{Leonhardt A}, Borst A (2016). Comprehensive Characterization of the Major Presynaptic Elements to the \textit{Drosophila} OFF Motion Detector. \textit{Neuron} 89(4):829-41.
    
    \begin{itemize}
        \item
        % \paragraph{Contributions}
        E.S.\ and M.M.\ jointly performed and evaluated all calcium imaging and electrophysiology experiments. \textbf{A.L.}\ performed and evaluated the behavioral experiments. \textbf{A.L.}\ and A.B.\ performed computer simulations. A.B., E.S., and M.M.\ designed the study. E.S.\ and M.M.\ wrote the manuscript with the help of the other authors. E.S.\ and M.M.\ contributed equally to this article.
    \end{itemize}
    
    \item \textbf{Leonhardt A}, Ammer G, Meier M, Serbe E, Bahl A, Borst A (2016). Asymmetry of \textit{Drosophila} ON and OFF motion detectors enhances real-world velocity estimation. \textit{Nature Neuroscience} 19(5):706-15.
    
    \begin{itemize}
        \item
        % \paragraph{Contributions}
        \textbf{A.L.}, G.A.\ and A.\ Borst designed the study. \textbf{A.L.}\ performed behavioral experiments, associated data analysis and all modeling work. G.A., M.M.\ and E.S.\ performed electrophysiological experiments. G.A.\ performed calcium imaging. \textbf{A.L.}\ and G.A.\ analyzed physiological data. A.\ Bahl designed the behavioral apparatuses and performed behavioral experiments. \textbf{A.L.}\ wrote the manuscript with help from all of the authors. \textbf{A.L.}\ and G.A.\ contributed equally to this article.
    \end{itemize}
    
\end{itemize}

\vspace{15mm}

  \begin{minipage}[t]{0.5\linewidth}
    \sign{Aljoscha Leonhardt}
    % \par 
    % Munich, Date
  \end{minipage}
  \begin{minipage}[t]{0.5\linewidth}
    \raggedright
    \sign{Georg Ammer}
    \par
    Co-author
  \end{minipage}%
  
  \vspace{5mm}
  
    \begin{minipage}[t]{0.5\linewidth}
    \sign{Prof. Dr. Alexander Borst}
    \par 
    Supervisor
  \end{minipage}

\newpage