\chapter*{Curriculum vitae}

\section*{Education}

\begin{itemize}
    \item 2012--present: PhD student at Graduate School for Systemic Neurosciences (LMU Munich)/Max-Planck-Institute for Neurobiology, Germany; supervised by Alexander Borst
    
    \item 2011--2012: Preparatory year in Neuroscience at Graduate School for Systemic Neurosciences (LMU Munich), Germany
    
    \item 2008--2011: BA in Natural Sciences at University of Cambridge, UK
    
    \item 2007: Abitur at Gymnasium Gars, Germany
\end{itemize}

\section*{Conferences \& Meetings}

\begin{itemize}
     \item 2017: Poster presentation at Cosyne (Salt Lake City, US)
     \item 2016: Poster presentation at FENS Meeting (Copenhagen, Denmark)
     \item 2015: Poster presentation at Janelia Insect Vision Conference (Ashburn, US)
     \item 2015: Talk for Max-Planck-Center Symposium at Hebrew University (Jerusalem, Israel)
     \item 2014: Poster presentation at FENS Meeting (Milan, Italy)
\end{itemize}

\section*{Teaching}

\begin{itemize}
     \item Teaching assistant for \textit{Methods in Animal Physiology} in 2014, 2016, and 2017 (LMU Munich)
     \item Teaching assistant for \textit{Advanced Scientific Programming} in 2014 (LMU Munich)
\end{itemize}

\section*{Personal information}

\begin{itemize}
     \item Birthday: 30\textsuperscript{th} November 1988
     \item Nationality: German
     \item Languages: German (native), English (fluent)
     \item Programming languages: Python, MATLAB, LaTeX (expert); Java, C, Scala (experienced)
\end{itemize}

\section*{Publications}

\begin{itemize}
     
    \item \textbf{Leonhardt A}, Ammer G, Meier M, Serbe E, Bahl A, Borst A (2016). Asymmetry of \textit{Drosophila} ON and OFF motion detectors enhances real-world velocity estimation. \textit{Nature Neuroscience} 19(5):706-15.
    
    \item Serbe E, Meier M, \textbf{Leonhardt A}, Borst A (2016). Comprehensive Characterization of the Major Presynaptic Elements to the \textit{Drosophila} OFF Motion Detector. \textit{Neuron} 89(4):829-41.
        
    \item Ammer G, \textbf{Leonhardt A}, Bahl A, Dickson BJ, Borst A (2015). Functional Specialization of Neural Input Elements to the \textit{Drosophila} ON Motion Detector. \textit{Current Biology} 25(17):2247-53.
        
    \item Sobolev A, Stoewer A, \textbf{Leonhardt A}, Rautenberg PL, Kellner CJ, Garbers C, Wachtler T (2014). Integrated platform and API for electrophysiological data. \textit{Frontiers in Neuroinformatics} 8:32.
    
    \item Maisak MS, Haag J, Ammer G, Serbe E, Meier M, \textbf{Leonhardt A}, Schilling T, Bahl A, Rubin GM, Nern A, Dickson BJ, Reiff DF, Hopp E, Borst A (2013). A directional tuning map of \textit{Drosophila} elementary motion detectors. \textit{Nature} 500(7461):212-6.
    
\end{itemize}